```{r}
library(tidyverse)
library(caret)
library(rpart)
library(RWeka)
```

```{r}
csgo_round <- read.csv("csgo_round_snapshots.csv")
glimpse(csgo_round)
```

# Data Cleaning

- Don't need money columns
- Don't need players_alive since we are only using first screenshot
- Don't need health since we are only using first screenshot where it's constant
- Group like weapons

# Determining Round Number

```{r}
# Find out when a new round starts
csgo_round <- csgo_round %>% mutate(round_num=case_when(time_left > lag(time_left, 1) & (time_left - lag(time_left) > 5.0) ~ 'New Round', TRUE ~ "Same Round")) %>% relocate(round_num, .before=time_left)

# The first row is always a new round
csgo_round[1,"round_num"] <- 'New Round'

# Delete columns we do not need
unwanted_cols <- c("round_num", "ct_money", "t_money", "ct_players_alive", "t_players_alive", "ct_money", "t_money", "time_left", "ct_health", "t_health")

csgo_round <- csgo_round[csgo_round$round_num == 'New Round',] %>% select(!all_of(unwanted_cols))

# Group weapons

all_grenades <- c("grenade_hegrenade", "grenade_flashbang", "grenade_smokegrenade", "grenade_incendiarygrenade", "grenade_molotovgrenade", "grenade_decoygrenade")

csgo_round$t_grenades <- rowSums(csgo_round[,paste0("t_", all_grenades)])
csgo_round$ct_grenades <- rowSums(csgo_round[,paste0("ct_", all_grenades)])

csgo_round <- csgo_round %>% select(-contains(all_grenades))

all_pistols <- c("weapon_glock", "weapon_usps", "weapon_p250", "weapon_tec9", "weapon_p2000", "weapon_fiveseven", "weapon_cz75auto", "weapon_deagle", "weapon_r8revolver", "weapon_elite")
special_pistols <- c("weapon_p250", "weapon_tec9", "weapon_fiveseven", "weapon_cz75auto", "weapon_deagle", "weapon_r8revolver", "weapon_elite")

csgo_round$t_pistols <- rowSums(csgo_round[,paste0("t_", special_pistols)])
csgo_round$ct_pistols <- rowSums(csgo_round[,paste0("ct_", special_pistols)])

csgo_round <- csgo_round %>% select(-contains(all_pistols))

all_shotguns <- c("weapon_nova", "weapon_xm1014", "weapon_mag7", "weapon_sawedoff")

csgo_round$t_shotguns <- rowSums(csgo_round[,paste0("t_", all_shotguns)])
csgo_round$ct_shotguns <- rowSums(csgo_round[,paste0("ct_", all_shotguns)])

csgo_round <- csgo_round %>% select(-contains(all_shotguns))

all_smgs <- c("weapon_mac10", "weapon_mp9", "weapon_ump45", "weapon_mp7", "weapon_bizon", "weapon_p90", "weapon_mp5sd")

csgo_round$t_smgs <- rowSums(csgo_round[,paste0("t_", all_smgs)])
csgo_round$ct_smgs <- rowSums(csgo_round[,paste0("ct_", all_smgs)])

csgo_round <- csgo_round %>% select(-contains(all_smgs))

all_rifles <- c("weapon_galilar", "weapon_famas", "weapon_ak47", "weapon_m4a4", "weapon_m4a1s", "weapon_sg553", "weapon_aug")

csgo_round$t_rifles <- rowSums(csgo_round[,paste0("t_", all_rifles)])
csgo_round$ct_rifles <- rowSums(csgo_round[,paste0("ct_", all_rifles)])

csgo_round <- csgo_round %>% select(-contains(all_rifles))

all_snipers <- c("weapon_ssg08", "weapon_awp", "weapon_g3sg1", "weapon_scar20")

csgo_round$t_snipers <- rowSums(csgo_round[,paste0("t_", all_snipers)])
csgo_round$ct_snipers <- rowSums(csgo_round[,paste0("ct_", all_snipers)])

csgo_round <- csgo_round %>% select(-contains(all_snipers))

all_machines <- c("weapon_m249", "weapon_negev")

csgo_round$t_machines <- rowSums(csgo_round[,paste0("t_", all_machines)])
csgo_round$ct_machines <- rowSums(csgo_round[,paste0("ct_", all_machines)])

csgo_round <- csgo_round %>% select(-contains(all_machines))

csgo_round <- csgo_round %>% relocate(round_winner, .after=last_col())

# Write the new data to a CSV
#write.csv(csgo_round, "csgo_test.csv")
```

# Making all character vectors into factors

```{r}
csgo_round <- csgo_round %>% mutate_if(is.character, as.factor)
csgo_round<-subset(csgo_round, select = -c(ct_score, t_score))
```

# Downsize simple

```{r}
set.seed(9)
csgo_round_ds<-sample_n(csgo_round,1000)

```

# SVM Model

```{r, eval=FALSE}
library(kernlab)# for SVM
library(e1071) # also for SVM
library(randomForest)
library(RColorBrewer)
library(FSelector)#information.gain


##Finding features
info<-information.gain(round_winner~., data = csgo_round)#find the importance attributes
info<- cbind(attributes = rownames(info), info)#make index names into a column 





################################################################################
# fit Support Vector Machine model
```{r pressure, echo=FALSE}

svmfit = svm(round_winner ~ ., data = csgo_round_ds,
             kernel = 'linear',
             scale = FALSE)

pred.svm = predict(svmfit, newdata = csgo_round_ds)
confusionMatrix(pred.svm, csgo_round_ds$round_winner)


#save model
saveRDS(svmfit, 'svmfit.rds')


# read in saved model
svmfit = readRDS('svmfit.rds')

################################################################################
#SVM with Linear Kernel


search.grid = expand.grid(C = seq(0.1, 2, length = 20))

# set up fold cross validation 
train.control = trainControl(
  method = 'repeatedcv', 
  number = 4
  )

svm.m1 = train(round_winner ~.,
               data = csgo_round_ds,
               method = 'svmLinear',
               trControl = train.control,
               tuneGrid = search.grid)


# results for the best model
confusionMatrix(svm.m1)


#save model
saveRDS(svm.m1, 'svm.m1.rds')


# read in saved model
svm.m1 = readRDS('svm.m1.rds')

################################################################################
# SVM with Polynomial Kernel(not run)



search.grid = expand.grid(degree = c(1, 2, 3),
                          scale = c(0.001, 0.01, 0.1, 1.0),
                          C = seq(0.1, 2, length = 20))

train.control = trainControl(
  method = 'repeatedcv', 
  number = 4
  )


svm.m2 = train(round_winner ~.,
                data = csgo_round_ds,
                method = 'svmPoly',
                trControl = train.control,
                tuneGrid = search.grid)

# results for the best model
confusionMatrix(svm.m2)


#save model
saveRDS(svm.m2, 'svm.m2.rds')


# read in saved model
svm.m2 = readRDS('svm.m2.rds')


```

##Random Forest

```{r}

search.grid = expand.grid(.mtry = (1:5)) 

rf.m1 = train(round_winner ~.,
              data = csgo_round_ds,
              method = 'rf',
              metric = 'Accuracy',
              trControl = train.control,
              tuneGrid = search.grid)



# results for the best model
confusionMatrix(rf.m1)

```


###k-NN algorithm

```{r}
# odd numbers so we don't have ties
search.grid = expand.grid(k = seq(5, 25, 2)) 

# set up 3-fold cross validation 10 times
train.control = trainControl(
  method = 'repeatedcv', 
  number = 3
  )

# train model
knn = train(round_winner ~ .,
  data = csgo_round_ds,
  method = 'knn',
  trControl = train.control,
  tuneGrid = search.grid
  )

